Data acquisition can take many forms, nd measure a huge range of effects/properties eg. Voltage,
current, light intensity etc. One of the most common data acquisition components is an ADC. There
are several common ADC types including Flash, Sigma-Delta ($\sum-\Delta$), CODECs, Successive
approximation and integrating ADCs.

\subsection{Ideal v. Practical Sampling}
Ideal sampling would have an input signal which would be sampled using convultion with a time domain
driac comb (series of delta functions) offset by the sample interval $f(x)=\sum_{k=0}^N \delta(x-k)$.
However, this is not realisable as a voltage impulse cannot be created without an $\infty$ current
therefore the sampling waveform looks more similar to a low duty cycle pulse signal with a pulse
width of $T_0$ and a sampling period of $T_s=1/2W$

\subsection{Uniform Quantisation}
An N-bit uniform quantisation has $2^N$ levels to match a continuos input analog voltage to a
quantised digital output.

\begin{itemize}
    \item Quantisation Interval: $\Delta = (V_{\textrm{max}} - V_{\textrm{min}})/2^N$
    \item Quantisation Error: $V_{err} \in [-\Delta / 2, \Delta / 2]$
    \item Variance of Error: $\Delta ^2/12$ 
    \item SNR: $10log_{10} (\frac{(V_{\textrm{max}}-V_{\textrm{min}})^2/8}{\Delta ^2/12}$)
\end{itemize}

\subsection{FLASH Quantisation}
FLASH Quantisation uses a resistor ladder and comparators to determine the analog input voltage of a
signal. This type of quantisation is the fastest however the accuracy is poor. The structure of a
FLASH quantiser is shown in Figure \ref{fig:flash-quant}.

\input{Term 2/figures/flash-quant.tex}

\subsection{Sigma-Delta ADC ($\sum - \Delta$ ADC)}
The sigma-delta ($\sum - \Delta$) ADC is uses summing and integration to determine the value of the
analog input. This significantly decreases the effect of quantisation noise as it acts as high pass
filter for the noise, skewing it into higher frequencies outside of the digital filter passband. A
block diagram for the sigma delta ADC is shown in Figure \ref{fig:sig-delt}.

\input{Term 2/figures/sig-delt.tex}

\subsubsection{Importance of Oversampling}
Sigma Delta ADC's must oversample to ensure accuracy of data collection eg. if not oversampling
enough there cannot be a distinction between different rates of change. This occurs when the slopes
are extremely steep causing the Sigma Delta to fall behind in its estimate if many of these high
frequency changes occur the ADC can experience issues with increasing error.

\subsubsection{Digital Filter}
The Digital Decimation Filter performs digital low pass filtering on the output signal, this removes
all of the high frequency quantisation noise and leaves just the output bit stream.

\subsubsection{Noise Shaping}
The integrator acts a high pass filter for the noise, therefore it pushes the noise into higher
frequencies. This noise is then able to be removed in the digital filtering stage.
