\subsection{Block Processing}
Block processing is where the CPU processes the data blocks already stored in memory, together
without streaming more data. This is usually done with the data in vector form, see Intel AVX
instructions and ARM Neon intrinsics. An example of block processing could be a moving average
filter (MAF). For the moving average filter once it has been applied to the input data the output
must be stored in a separate memory section. This can pose issues in moving within memory and
between memory and peripherals.

\subsection{Unbuffered Data Transfer}
Unbuffered transfer is when no buffer is implemented on the input of data, this can cause
synchronization issues as both the sender and receiver need to be aware of the when the data is
transferred. A diagram of this is shown in Figure \ref{fig:unbuffered}\\

\noindent There are two methods for implementing unbuffered transfer, the first is to use
\textit{Polling}. Polling can waste CPU cycles as the CPU will have to reguarly check if data is
available. This can be somewhat mitigated through the use of the second method, \textit{Interrupts}
this method ensures that data can be transferred once it is available however, there can be
significant overhead created due to the context switch required to service the interrupt.

\input{Term 2/figures/unbuffered.tex}

\subsection{Buffered Data Transfer}
By using a buffer a block of data can be transferred once the FIFO (First in First out) buffer is
full. To indicate that the buffer is full an ISR (Interrupt Service Routine) can be used. This
reduces the overhead as interrupts are occurring less frequently than with unbuffered however, there
is a latency increase as data is held until the buffer is full. This method can also be used to
transfer data without the CPU. Figure \ref{fig:buffered} shows the general format of a buffered data
transfer.

\input{Term 2/figures/buffered.tex}

\subsection{Transfer Interfaces}
There are several method to achieve high speed CPU independent data transfer between memory sections
or between memory and peripherals these include:

\begin{itemize}
    \item Host port interface (This is a MCU to MCU interface/parallel address bus, this is rare now)
    \item Buffered Serial Port (This is a peripheral to memory transfer)
    \item Dual Port Memory (This has simultaneous read and write access)
    \item Direct Memory Access (This is a programmable and cascadeable module)
\end{itemize}

\subsubsection{Dual-Port Memory}
Dual port memory (shown in Figure \ref{fig:dual-port-mem}) allows for similtaneous read/write memory
operations, to achieve this arbitration logic is required to control memory access confilicts. The
applications for this are DSP active filters and shared memory systems.

\input{Term 2/figures/dual-port-mem.tex}

\subsubsection{Direct Memory Access}
Direct Memory Access (DMA) is a data transfer system that requires very little CPU intervention and
can handle I/O to memory and memory to memory transfers a typical configuration for this is shown in
Figure \ref{fig:dma-config}.

\input{Term 2/figures/dma-config.tex}

\subsubsection{DMA Controller}
The DMA controller is a bus mastering device which means it is able to perform read/write operations
independent of the CPU. To perform a I/O to memory DMA the peripheral signals the DMA via an
interrupt, the DMA controller then responds to the peripheral and reads the data. The DMA then uses
the transfer count (TC) register to determine how the number of samples into an allocated memory
section. The DMA then informs the CPU of the completed transfer via interrupt.\\

\noindent The structure of the registers in the DMA are shown in Figure \ref{fig:dma-reg}

\input{Term 2/figures/dma-reg.tex}

\subsubsection{DMA Chaining}
DMA's can be chained, this is were the descriptor points to a control block in memory. The control
block is loaded automatically by DMA chaining to start a DMA session. DMA chaining uses a linked
list structure. DMA chaining is shown in Figure \ref{fig:dma-chain}. As the values in the DMA
registers are memory mapped the DMA descriptors can be chained together with pointers. DMA chaining
can be use the achieve a ping pong buffer format, with the second DMA referring to the next buffer
and switching automatically once the transfer count is complete.

\input{Term 2/figures/dma-chain.tex}

\subsubsection{Ping-Pong Buffer}
The Ping Pong buffer, shown in Figure \ref{fig:ping-pong} is a simple buffering system that has two
buffers on the input and output of the processor. This arrangement maximises the processing efficiency
of the processor as data can always be made available and there is always a location to write output
data to.

\input{Term 2/figures/ping-pong.tex}
