\subsection{Serial interfaces vs parallel interfaces}
\begin{itemize}
    \item Serial interfaces
        \begin{itemize}
            \item Encode bits by their temporal locations in the transmission medium
            \item Suitable for pin-limited devices
        \end{itemize}
    \item Parallel interfaces
    \begin{itemize}
        \item Encoded use spacial locality
    \end{itemize}
    \item Issues
    \begin{itemize}
        \item How does the device know when to start looking for information?
        \item What is the bit order?
        \item How does the receiver know when the transmission is complete?
    \end{itemize}
\end{itemize}

\subsection{Simplex, Full-Duplex and Half-Duplex}
\input{Term 2/figures/simplex-duplex.tex}

\subsection{Asynchronous vs Synchronous}

\noindent \textbf{NOTE}: This is NOT required for analogue communications.

\begin{itemize}
    \item Asynchronous
    \begin{itemize}
        \item No clock signal transmitted
        \item Each end has a clock with the same \textit{nominal} frequency
        \item Clock and frame synchronization is required
    \end{itemize}
    \item Synchronous
    \begin{itemize}
        \item Clock is sent over a separate wire
        \item Clock signal is encoded within data (eg. Manchester Code)
    \end{itemize}
\end{itemize}

\subsection{Manchester Code}
With non-return to zero (NRZ) coding, clock synchronization would be difficult during long sequences
of either `1' of `0'. Manchester Code negates this by using the voltage transition to represent `1'
and `0'.
\input{Term 2/figures/manchester-code.tex}

\subsection{Serial Interface Comparison}
\input{Term 2/figures/serial-interfaces.tex}

\input{Term 2/figures/serial-interface-comp-flow.tex}

\subsection{RS-232 vs RS-485}
\input{Term 2/figures/rs232vsrs485.tex}

\subsection{SSI}
Synchronous Serial Interface (SSI) operates with a master slave model and is based off RS-422, is
point to point and used frame syncronization.

\input{Term 2/figures/ssi.tex}

A single SSI transmission is shown in Figure \ref{fig:ssi-wave}, to send multiple transmissions a
frame sync signal is sent on the LSB and the next transmission is sent.
\input{Term 2/figures/ssi-wavforms.tex}

\subsection{SPI}
Serial Peripheral Interface (SPI), uses a master-slave model, is single ended, duplex, multipoint
and uses selection line based framing.

\input{Term 2/figures/spi.tex}
SPI can be considered a simplified version of SSI, without frame synchronisation. The waveform for
the SPI protocol is shown in Figure \ref{fig:spi-wave}

\subsection{UART}
Universal Asynchronous Receive Transmit (UART) is a simple full duplex asynchronous serial
interface. UART has not framing beyond a single byte and required matched settings at both the
receiver and transmitter to avoid incorrect communications. UART has relatively high overheads and
can operate at most at 80\% efficiency. UART is also a free form protocol so can be adapted in
software to suit the application.

\input{Term 2/figures/spi-wave.tex}

\subsection{I$^2$C/TWI}
Inter-integrated circuit (I$^2$C) or Two wire interface (TWI) is a simple, robust a d easy to use
communication system for use between a microcontroller and several external peripherals (bus type
protocol). I$^2$C is availible in standard speed at 100kbps, full-speed at 400kbps and high-speed
at 3.33Mbps. The bus supports up to 127 devices in parallel. The protocol is half duplex and
synchronous (\textit{More complicated than SPI with slave select}). This protocol is robust as every
byte has an ACK response to verify the receipt of the message, there is also built in arbitration to
eliminate bus conflicts using Carrier sense multiple access/collision detection.\\

\noindent The protocol uses 8-bit words and master slave handshaking where the master generates the clock
signal and initiates the communication. Within the transmission there is an address byte for device
selection, a read write bit for declaring reading and writing operations.\\

\subsubsection{Clock Stretching}
Clock stretching is when a slow slave device pulls the clock line low until it is ready to transmit
data, this allows the slower device to send at a usable rate for its application.

\input{Term 2/figures/i2c-osi.tex}

The process of a master to slave transmission is shown in Figure \ref{fig:i2c-master-slave}.

\input{Term 2/figures/i2c-master-slave.tex}

\subsubsection{I$^2$C Write}
To write to a slave the send the start condition and starts the clock then send the 7-bit slave
address with the MSB first. The master then send the `0' write bit the slave then responds with an
ACK (`0'). The master then sends data (This can be several bytes). The slave then sends an ACK (`0')
and finally the master sends the stop condition.

\subsubsection{I$^2$C Read}
To read from a slave the master sends the start condition then starts the clock. The 7-bit slave
address is then transmitted with MSB first. To indicate a read the master then sends a `1' read bit.
The selected slave then responds with a ACK (`0'). The slave then sends the appropriate bit stream
(This can be several bytes). The master finally responds with a NACK then the stop condition.\\ 

\noindent To complete a full read from an external sensor the master must frist perform a write
operation to the slave then perform a read.

\subsubsection{Packet Structure}
The packet structure of I$^2$C is shown in Figure \ref{fig:serial-packet}, This is for writing, to
preform a read operation the R/W bit is set to `1' to indicate a read and in the data byte a NACK is
used instead of the ACK (\textit{ACK=1, NACK=0}). 
\input{Term 2/figures/serial-packet.tex}

\subsubsection{Multi-master Operation}
Multi-master operation is supported on I$^2$C however, in this mode arbitration is required as
several masters may attempt to control the bus simultaneously. For this to work every master in a
multi-master must be configured to a multi-master setup as single masters don't arbitrate, causing
interference if a single master is connected. The master device controls SDA and SCK.

Arbitration simply allows the faster (or slower) device to access the channel. To detect if the
channel is in use the SDA and SCL lines are checked to see if they are LOW.

\subsubsection{Collision Detection}
A collision is where more than one device is transmitting on the SDA line at once. To perform
collision detection a device has to be able to read the SDA line while checking the SDA for
transmitted bits. And if the two don't match then a collision has occurred. This is determined using
the XOR of the requested bit and the line data, shown in Figure \ref{fig:collision-detect}.

\input{Term 2/figures/collision-detect.tex}
